Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-26 chapters/introduction/introduction.tex
add an image to the dissertation

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to
this such a vision task as {\em geo-calibration}.
In current work of geo-calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some 
drawbacks: 1) Deterministic systems can not handle uncertainties in
the real world very well. 2) they are not
friendly to applications developed with graphic models that are
interfaced with their outputs. To address these problems, We propose
to build probabilistic models for camera geo-calibration.

Beside that, we also explored the possibility to learn high-level
features from the networks that do geo-calibration. \todo{expand}

@@

\subsection{Deep Neural Networks for Geo-Calibration}
In recent years, deep neural networks (DNNs) rise as stars. Methods
using DNNs have achieved state-of-the-art performances in many computer
vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
information, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from aerial imagery that can be matched to features extracted
from ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geolocalization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image.  Horizon line is
important indicator for estimating camera poses.
Work~\cite{workman2016horizon, hold2017perceptual} has been done to to
identify the horizon line using an end-to-end CNN. Workman
\etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
neural network that can do 6-DOF camera relocalization, but their
method only limited to specific scenes.

\subsection{Cross-view Imagery}
Since the cross-view imagery plays an important role in geolocalization,
we spare an seperate section to introduce it. The cross-view image
pair consists of a ground-view image and an overhead imager at the
same location. In some cases, the ground/overhead images are also
aligned in orientation.
Specifically, Study of the overhead imagery has been long started.
Efforts have been made to automate overhead image analysis. As early
as 1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
obtain the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.
Given the fact that overhead imagery has much larger earth coverage
and better registered in geographic locations, many geo-localization
approaches extract the features of it as reference
database~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}

Furthermore, there are many other properties of the cross-view pairs
to explore for high-level feature extraction \todo{expand}.

\section{Our Approach}
We divide our approach in two steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions that describe the fitness between the calibration
parameters and the images. Under this guidance we dismantle the full
geo-calibration into several partial geo-calibration tasks, each of
which provides a constraint function that could fit into our general
model.

>>>>

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to 
such a vision task as {\em geo-calibration}.
In current work of geo-calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some 
drawbacks: 1) Deterministic systems can not handle uncertainties in
the real world very well. 2) they are not
friendly to applications developed with graphic models that are
interfaced with their outputs. To address these problems, We propose
to build probabilistic models for camera geo-calibration.

Beside geo-calibration, this thesis also studies the possibility to
learn high-level image representations with help of geographic
information. In one of our work, we demonstrate that we are able to
learn geo-temporal feature representations of image with geographic
locations and capture time. In another work, knowing the geographic
location, we transfer the learned knowledge of a CNN for ground image
segmentation to another CNN designed for overhead image segmentation.

\begin{figure}
  \centering
  \includegraphics[width=.8\linewidth]{introduction/architecture}
  \caption{Architecture of our approach.}
  \label{fig:intro:architecture}
\end{figure}

@@

\subsection{Deep Neural Networks for Geo-Calibration}
In recent years, deep neural networks (DNNs) rise as stars. Methods
using DNNs have achieved state-of-the-art performances in many computer
vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to features extracted
from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geolocalization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image.  Horizon line is an
important indicator for estimating camera poses.
Work~\cite{zhai2016horizon, workman2016horizon, hold2017perceptual}
has been done to to identify the horizon line with CNNs.
Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate
the camera focal length. Kendall \etal~\cite{kendall2015convolutional}
propose a neural network that can identify 6-DOF camera parameters,
but their method only limited to specific scenes.

\subsection{Cross-view Imagery}
Since the cross-view imagery plays an important role in geolocalization,
we spare an separate section to introduce it. A cross-view image
pair consists of a ground-view image and an overhead image at the
same location. In some cases, the ground/overhead images are also
aligned in orientation.
Specifically, Study of the overhead imagery has been long started.
Efforts have been made to automate overhead image analysis. As early
as 1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
obtain the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.
Given the fact that overhead imagery has much larger earth coverage
and better registered in geographic locations, many geo-localization
approaches~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
extract the overhead features as reference database for
geo-localization.

%Furthermore, there are many other properties of the cross-view pairs
%to explore for high-level feature extraction \todo{expand}.

\section{Our Approach}
We divide our approach in two steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions that describe the fitness between the calibration
parameters and the images. Under this guidance we dismantle the full
geo-calibration into several partial geo-calibration tasks, each of
which provides a constraint function that could fit into our general
model. The architecture of our approaches refers to
\figref{intro:architecture}.
